EDA

### 2021-04-27 Manuscript_AB_MP.Rmd
Clean up data files, include new random effects models for beta

We

@@

```{r exp1_descriptive_rt_table, as.is = TRUE,echo=FALSE}
#load raw Exp1 data
exp2 <- read_csv("Exp 1 data.csv")
exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

exp1$StimulusType <- factor(exp1$StimulusType, levels = c("NW", "WORD"), labels = c("Nonword", "Word"))
exp1$Condition <- factor(exp1$Condition, levels = c("ID", "UN"), labels = c("Identical", "Unrelated"))
exp1$PrimeDuration <- factor(exp1$PrimeDuration, levels = c(33, 50), labels = c("33 ms", "50 ms"))

exp1_descriptives_rt <- exp1 %>%
  filter(rt > 250 & rt < 2000 & corr == 1) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Mean = mean(rt)
    , Median = median(rt)
    , SD = sd(rt)
    , Min = min(rt)
    , Max = max(rt)
  )

exp1_descriptives_corr <- exp1 %>%
  filter(rt > 250 & rt < 2000) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Accuracy = mean(corr)
  )

apa_table(
  exp1_descriptives_rt
  , caption = "(ref:exp2-descriptives-rt-table-caption)"
  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
  , escape = TRUE
)  
```
We

(ref:exp1-blmm-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.

```{r load_exp1_brms_data, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp1_rt_new.RData")
# model name is blmm_exp1_rt

@@

blmm_exp2_summary <- summary(blmm_exp2_rt)

blmm_exp2_fixed_for_print <- blmm_exp2_summary$fixed

@@

blmm_exp1_fixed_for_print <- blmm_exp2_fixed_for_print %>% tibble(Parameter = parameter_names, .)

colnames(blmm_exp2_fixed_for_print) <- c("mean","SE","lower bound","upper bound","Rhat", "Bulk ESS","Tail ESS")

blmm_exp2_fixed_for_print <- blmm_exp2_fixed_for_print  %>%
  dplyr::select(-ends_with("ESS"))

write.csv(blmm_exp2_fixed_for_print, file = "Table_3.csv", row.names = FALSE)

apa_table(
    blmm_exp1_fixed_for_print,
    placement = "H",
    align = c("c", "c", "c", "c", "c"),
    caption = "(ref:exp2-blmm-table-caption)",
    note = NULL,
    small = TRUE,
    digits = 3,
    escape = FALSE
    )

```
## Discussion

$\hat{R}$

@@

```{=html}
<script src="https://hypothes.is/embed.js" async></script>
```
\newpage

>>>>

@@

```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE}

exp2_descriptives_rt <- exp2_data_to_include %>%
  filter(rt > 250 & rt < 2000 & corr == 1) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Mean = mean(rt)
    , Median = median(rt)
    , SD = sd(rt)
    , Min = min(rt)
    , Max = max(rt)
  )

exp2_descriptives_corr <- exp2_data_to_include %>%
  filter(rt > 250 & rt < 2000) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Accuracy = mean(corr)
  )

exp2_descriptives_rt[, -1] <- printnum(exp2_descriptives_rt[, -1], digits = 0)

exp2_descriptives_corr[, -1] <- printnum(exp2_descriptives_corr[, -1], digits = 2)

colnames(exp2_descriptives_rt)[1:2] <- c("Stimulus Type", "Prime Duration")

exp2_descriptives_rt$Accuracy <- exp2_descriptives_corr$Accuracy

apa_table(
  exp2_descriptives_rt
  , caption = "(ref:exp2-descriptives-rt-table-caption)"
  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
  , escape = TRUE
)  
```

(ref:exp2-blmm-rt-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 2.

```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp2_rt_new.RData")
# model name is blmm_exp1_rt

@@

blmm_exp2_summary_rt <- summary(blmm_exp2_rt)

blmm_exp2_rt_fixed_for_print <- blmm_exp2_summary_rt$fixed

@@

blmm_exp2_rt_fixed_for_print <- blmm_exp2_rt_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
  dplyr::select(-ends_with("ESS"))

write.csv(blmm_exp2_rt_fixed_for_print, file = "Table_3.csv", row.names = FALSE)

apa_table(
    blmm_exp2_rt_fixed_for_print,
    placement = "H",
    align = c("c", "c", "c", "c", "c"),
    caption = "(ref:exp2-blmm-rt-table-caption)",
    note = NULL,
    small = TRUE,
    digits = 3,
    escape = FALSE
    )

The model indicates that response times were higher in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1","u-95% CI"]`]), although across the two prime duration conditions, the effect was much smaller than in Experiment 1. Response times were also higher in the 16 ms than in the 33 ms prime duration condition (*b* = `r blmm_exp2_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]) although, as the interaction effect shows, this was mainly due to an absence of the priming effect in the 16 ms prime duration condition, as opposed to the 33 ms condition, which showed a robust priming effect (*b* = `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]). Figure \@ref(fig:exp2-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.

(ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 2.

```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)"}

del_hdi_exp2_rt = hdi(blmm_exp2_rt, ci = c(0.5, 0.75, 0.89, 0.95))
# brms (like any other lm-like function) automatically adds a "1" to the parameter name (for the contrast)
# get rid of the ones (and any other numbers) by using gsub 
#del_hdi_exp2_rt$Parameter <- del_hdi_exp2_rt$Parameter %>% gsub(pattern = "[[:digit:]]", replacement = "")
plot(del_hdi_exp2_rt) + scale_fill_flat() + theme_apa()
```

(ref:exp2-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 2.

```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE}

load("blmm_exp2_acc_new.RData")

blmm_exp2_summary_acc <- summary(blmm_exp2_acc)

blmm_exp2_acc_fixed_for_print <- blmm_exp2_summary_acc$fixed

blmm_exp2_acc_fixed_for_print <- blmm_exp2_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
  dplyr::select(-ends_with("ESS"))

write.csv(blmm_exp2_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)

apa_table(
    blmm_exp2_acc_fixed_for_print,
    placement = "H",
    align = c("c", "c", "c", "c", "c"),
    caption = "(ref:exp2-blmm-accuracy-table-caption)",
    note = NULL,
    small = TRUE,
    digits = 3,
    escape = FALSE
    )

The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1","u-95% CI"]`]). The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 16 ms prime duration condition than in the 33 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp2_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]). The interaction term indicates that the expected effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) only present in the 33 ms condition, and reversed in the 16 ms condition (*b* = `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp2_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]), although the effect in the 16 ms condition was very weak.

## Discussion

In Experiment 2, we observed the pattern we expected from previous research: a robust priming effect in response time and accuracy in the 33 ms condition, but a very weak effect in the 16 ms condition. This suggests that the timing in our online experiments was likely to be quite close to the timing set in the experiment script.

@@

In this study, we

\newpage
